%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, a4paper]{article}

% Style derived from https://github.com/mrzool/cv-boilerplate

% LAYOUT
%--------------------------------
% Margins
\usepackage{geometry} 
\geometry{
  letterpaper,
  left=33mm,
  right=15mm,
  top=15mm,
  bottom=15mm,
  marginparwidth=25mm,
  marginparsep=3mm
}

% Do not indent paragraphs
\setlength\parindent{0in}

\pagenumbering{gobble}

% TYPOGRAPHY
%--------------------------------
\usepackage{fontspec} 
\usepackage{xunicode}
\usepackage{xltxtra}

% converts LaTeX specials (quotes, dashes etc.) to Unicode
\defaultfontfeatures{Mapping=tex-text}
\setromanfont [Ligatures={Common}, Numbers={OldStyle}]{Hoefler Text}

% Cool ampersand
\newcommand{\amper}{{\fontspec[Scale=.95]{Hoefler
Text}\selectfont\itshape\&}}

% Bodoni 72 Smallcaps Book

% MARGIN NOTES
%--------------------------------
\usepackage{marginnote}
\newcommand{\note}[1]{\marginnote{\raggedleft\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\reversemarginpar

% HEADINGS
%--------------------------------
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\rmfamily\mdseries} 
\subsectionfont{\rmfamily\mdseries\normalsize}%\scshape\normalsize} 
\subsubsectionfont{\rmfamily\mdseries\normalsize}%\upshape\normalsize}

\usepackage{titlesec}
\titlespacing*{\section}
{0pt}{5mm}{3mm}
\titlespacing*{\subsection}
{0pt}{3mm}{0.3mm}
\titlespacing*{\subsubsection}
{0pt}{2mm}{0.3mm}

% LISTS
%--------------------------------
\usepackage{enumitem}
\newlist{bullets}{enumerate}{1}
\setlist[bullets,1]{
  label=$\cdot$,
  itemsep=0.2mm,
  topsep=0.5mm,
  leftmargin=4mm,
  parsep=0.5mm,
}

% PDF SETUP
%--------------------------------
\usepackage{hyperref}
\hypersetup
{
  pdfauthor={Matthew Wetmore},
  pdfsubject={Matthew Wetmore's CV},
  pdftitle={Matthew Wetmore's CV},
  colorlinks, breaklinks, xetex, bookmarks,
  filecolor=black,
  urlcolor=[rgb]{0.117,0.682,0.858},
  linkcolor=[rgb]{0.117,0.682,0.858},
  linkcolor=[rgb]{0.117,0.682,0.858},
  citecolor=[rgb]{0.117,0.682,0.858}
}

% OTHER
%--------------------------------
\newcommand{\middot}{$\:\:\cdot\:\:$}
\newcommand{\loc}[1]{\textbf{#1}}

% Separate args with mid dots
\makeatletter
\newcommand{\dotsep}[1]{%
    #1\checknextarg}
\newcommand{\checknextarg}{\@ifnextchar\bgroup{\gobblenextarg}{}}
\newcommand{\gobblenextarg}[1]{\middot #1\@ifnextchar\bgroup{\gobblenextarg}{}}

% DOCUMENT
%--------------------------------
\begin{document}

{\Huge Matthew Wetmore}\\

\emph{%
Generalist with a background in theory and a decade of experience
creating interactive experiences. Detail-oriented and focused on building
reliable, maintainable, and fast software. Passionate about making tools people
love to use.
}\\

\setlength{\tabcolsep}{20pt}
\renewcommand{\arraystretch}{1.2}

\begin{tabular}{@{} l l l}
Glenside PA, 19038 & 267 992 6013 & \href{https://mattwetmore.me}{mattwetmore.me} \\
US Citizen & \href{mailto:wetmore.matt@gmail.com}{wetmore.matt@gmail.com} & \href{https://github.com/wetmore}{github.com/wetmore}\\
\end{tabular}

\section*{Work Experience}

\subsection*{\textbf{Independent Contracting}}
\subsubsection*{
  \note{\loc{Remote}\\May 2020 - Jun 2020}
  \dotsep
  {\emph{Venga}}
  {\href{https://www.gym.vengaclimb.com/}{vengaclimb.com}}
  {\emph{Tools used:} React Native, Expo, GraphQL}}
\begin{bullets}
  \item Introduced user profiles and follow functionality to a mobile app for
  climbing gym members.
\end{bullets}

\subsubsection*{
  \note{\loc{Remote}\\Apr 2020}
  \dotsep
  {\emph{Safety in Numbers}}
  {\href{https://safe7y.com/}{safe7y.com}}
  {\emph{Tools used:} Django, Vue.js}
}
\begin{bullets}
  \item Built custom web app for quick human-annotation of unstructured data
  needed for machine learning.
\end{bullets}

\subsection*{\dotsep{\textbf{Google}}{Software Engineer}}

\subsubsection*{
  \note{\loc{New York, NY}\\Aug 2016 - Apr 2018}
  \emph{Ephemeral Events}
}
\begin{bullets}
  \item Developed new search result UI elements for events such as Fashion Week
  (2016, 2017), the Academy Awards (2017), and the Winter Olympics (2018), and
  generalized them for use in other events.

  \item Designed and built a dashboard for monitoring traffic to team's
  features, providing insights such as which events were most popular or which
  queries were most popular for an event. This dashboard was essential to
  scaling feature rollout from a few events to thousands of events.
  
  \item Architected the data model and log aggregation pipeline underlying the
  dashboard. Gave particular care to ensuring the dashboard loaded quickly and
  its data model was ergonomic for writing one-off queries.
  
  \item Implemented a live countdown UI which appeared on the results page for
  upcoming events.
  
  \item Managed interns, and mentored new hires on other teams as part of
  employee mentoring program.
  
  \item Represented company in on-campus recruitment efforts.
\end{bullets}

\subsubsection*{
  \note{\loc{New York, NY}\\Sep 2015 - Sep 2016\\Summer 2014 (Intern)}
  \emph{Knowledge Exploration}
}
\begin{bullets}
  \item Introduced automatic support for right-to-left (RTL) languages to Oleo,
  an internal framework for creating ``immersive'' (interactive, app-like)
  search results.

  \item Launched immersive results for TV/music/film queries in Arabic- and
  Hebrew-speaking countries.

  \item Maintained Oleo and added new features used for the Google Trips UI and 
the 2016 Olympics experience.
\end{bullets}

\subsection*{
  \note{\loc{Montreal, QC}\\May 2013 - May 2014}
  \dotsep
  {\textbf{Scheduling Direct}}
  {Frontend Lead}
  {\emph{Tools used:} Backbone.js}
}
\begin{bullets}
  \item Architected and implemented the employee and manager user interfaces for
  a shift-scheduling application.
\end{bullets}

\subsection*{
  \note{\loc{New York, NY}\\Summer 2012}
  \dotsep
  {\textbf{Boxee}}
  {Intern}
  {\emph{Tools used:} D3.js, Backbone.js}
}
\begin{bullets}
  \item Developed interactive social graph visualization tool, used to
  analyze the growth of a new product.
\end{bullets}

\section*{Skills, Activities and Interests}

\subsection*{\textbf{Technology Skills}}
Javascript/ES6, Typescript, React, Vue, React Native, Python, Django, SQL,
Haskell, Java, Rust, Unix, Git, \LaTeX

\subsection*{\textbf{Activities}}
\note{May 2018 - Mar 2020}
Converted a cargo van into a mobile home, and lived in it while traveling North
America and rock climbing.

\subsection*{\textbf{Interests}}
Graphics, Generative art, Functional programming, Design, Rock
climbing, Snowboarding, Woodworking

\section*{Education}
\note{\textbf{McGill University\\Montreal, QC}\\2010 - 2015}
\subsection*{
  \dotsep
  {\textbf{B.Sc. (with Honours)} Mathematics \amper$\:$ Computer Science}
  {\textbf{Minor} Physics}
  {\textbf{GPA} $3.53$}
}
\emph{Favorite coursework:} Logic and Computation, Formal Verification,
Algorithm Design, Topology, Real Analysis
\end{document}
