%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, a4paper]{article}

% Style derived from https://github.com/mrzool/cv-boilerplate

% LAYOUT
%--------------------------------
% Margins
\usepackage{geometry} 
\geometry{
  letterpaper,
  left=33mm,
  right=15mm,
  top=14mm,
  bottom=14mm,
  marginparwidth=25mm,
  marginparsep=3mm
}

% Do not indent paragraphs
\setlength\parindent{0in}

\pagenumbering{gobble}

% TYPOGRAPHY
%--------------------------------
\usepackage{fontspec} 
\usepackage{xunicode}
\usepackage{xltxtra}

% converts LaTeX specials (quotes, dashes etc.) to Unicode
\defaultfontfeatures{Mapping=tex-text}
\setromanfont [Ligatures={Common}, Numbers={OldStyle}]{Hoefler Text}

% Cool ampersand
\newcommand{\amper}{{\fontspec[Scale=.95]{Hoefler
Text}\selectfont\itshape\&}}

% Bodoni 72 Smallcaps Book

% MARGIN NOTES
%--------------------------------
\usepackage{marginnote}
\newcommand{\note}[1]{\marginnote{\raggedleft\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\reversemarginpar

% HEADINGS
%--------------------------------
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\rmfamily\mdseries} 
\subsectionfont{\rmfamily\mdseries\normalsize}%\scshape\normalsize} 
\subsubsectionfont{\rmfamily\mdseries\normalsize}%\upshape\normalsize}

\usepackage{titlesec}
\titlespacing*{\section}
{0pt}{3mm}{2mm}
\titlespacing*{\subsection}
{0pt}{2mm}{0.3mm}
\titlespacing*{\subsubsection}
{0pt}{2mm}{0.3mm}

% LISTS
%--------------------------------
\usepackage{enumitem}
\newlist{bullets}{enumerate}{1}
\setlist[bullets,1]{
  label=$\cdot$,
  itemsep=0.2mm,
  topsep=0.5mm,
  leftmargin=4mm,
  parsep=0.5mm,
}

% PDF SETUP
%--------------------------------
\usepackage{hyperref}
\hypersetup
{
  pdfauthor={Matthew Wetmore},
  pdfsubject={Matthew Wetmore's CV},
  pdftitle={Matthew Wetmore's CV},
  colorlinks, breaklinks, xetex, bookmarks,
  filecolor=black,
  urlcolor=[rgb]{0.117,0.682,0.858},
  linkcolor=[rgb]{0.117,0.682,0.858},
  linkcolor=[rgb]{0.117,0.682,0.858},
  citecolor=[rgb]{0.117,0.682,0.858}
}

% OTHER
%--------------------------------
\newcommand{\middot}{$\:\:\cdot\:\:$}
\newcommand{\loc}[1]{\textbf{#1}}

% Separate args with mid dots
\makeatletter
\newcommand{\dotsep}[1]{%
    #1\checknextarg}
\newcommand{\checknextarg}{\@ifnextchar\bgroup{\gobblenextarg}{}}
\newcommand{\gobblenextarg}[1]{\middot #1\@ifnextchar\bgroup{\gobblenextarg}{}}

% DOCUMENT
%--------------------------------
\begin{document}

{\Huge Matthew Wetmore}\\

\emph{%
Generalist with a background in theory and expertise in Javascript development.
Focused on building reliable, maintainable, and fast software. Passionate about
making tools people love to use and creating interactive experiences.
}\\

\setlength{\tabcolsep}{20pt}
\renewcommand{\arraystretch}{1.2}

\begin{tabular}{@{} l l l}
New York, NY & \href{mailto:wetmore.matt@gmail.com}{wetmore.matt@gmail.com} &  \href{https://github.com/wetmore}{github.com/wetmore} \\
267 992 6013 & \href{https://mattwetmore.me}{mattwetmore.me} & \\
\end{tabular}

\section*{Work Experience}

\subsection*{
  \note{\loc{Remote}\\Oct 2020 - Aug 2021}
  \dotsep
  {\textbf{Kintaba} (\href{https://www.kintaba.com/}{kintaba.com})}
  {Software Engineer}
  {\emph{Tools used:} Typescript, React, Apollo GraphQL, PostgreSQL, Docker}
}

\begin{bullets}
  \item Third engineer in a 5-person startup creating an incident management SAAS.

  \item Led development of automations feature, which empowers users to write IFTTT-style
  rule-based responses to events in an incident lifecycle.
  
  \item Designed and created automation templates feature, allowing companies to add predefined
  automations.
  
  \item Added checklist functionality to Slate.js-based rich text editor for postmortems and incident comments.
 
  \item Created documents page, allowing users to search and filter postmortems for their
  company.
  
  %\item Optimized Webpack config to increase developer iteration speed.
\end{bullets}

\subsection*{
  \note{\loc{Remote}\\Apr 2020 - Jun 2020}
  \textbf{Independent Contracting}
}
\subsubsection*{
%  \note{\loc{Remote}\\May 2020 - Jun 2020}
  \dotsep
  {\emph{Venga} (\href{https://www.gym.vengaclimb.com/}{vengaclimb.com})}
  {\emph{Tools used:} Typescript, React Native, Styled Components, Expo, GraphQL, Storybook.js}}
\begin{bullets}
  \item Added user profiles and follow functionality to a mobile app for
  climbing gym members.
 % \item Made creating and maintaining UI components easier by introducing
 % Storybook.js to the development process.
\end{bullets}

\subsubsection*{
%  \note{\loc{Remote}\\Apr 2020}
  \dotsep
  {\emph{Safety in Numbers} (\href{https://safe7y.com/}{safe7y.com})}
  {\emph{Tools used:} Django, Vue.js (Javascript), Webpack}
}
\begin{bullets}
  \item Built custom web app for quick human-annotation of unstructured data
  needed for machine learning.
\end{bullets}

\subsection*{
  \dotsep
  {\textbf{Google}}
  {Software Engineer}
  {\emph{Tools used:} Javascript, Java, Python, GoogleSQL, Blaze, Closure Tools}
}

\subsubsection*{
  \note{\loc{New York, NY}\\Aug 2016 - Apr 2018}
  \emph{Ephemeral Events team (part of Search org)}
}
\begin{bullets}
  \item Developed new search result UI elements for events such as Fashion Week
  (2016, 2017), the Academy Awards (2017), and the Winter Olympics (2018), and
  generalized them for use in a generic component library.
  
  \item Worked with Cards Everywhere team to refine a new component library
  for building search elements.

  \item Designed and built a dashboard for monitoring traffic to team's
  features, providing insights such as which events were most popular or which
  queries were most popular for an event. This dashboard was essential to
  scaling feature rollout from a few events to thousands of events.
  
 % \item Architected the data model and log aggregation pipeline underlying the
  %dashboard. %Gave particular care to ensuring the dashboard loaded quickly and
  %its data model was ergonomic for writing one-off queries.
  
  %\item Implemented a live countdown UI which appeared on the results page for
  %upcoming events.
  
  \item Managed interns, and mentored new hires on other teams as part of
  employee mentoring program.
  
  \item Conducted on-site interviews and represented company in college campus
  recruitment efforts.
\end{bullets}

\subsubsection*{
  \note{\loc{New York, NY}\\Sep 2015 - Sep 2016\\Summer 2014 (Intern)}
  \emph{Knowledge Exploration team (part of Search org)}
}
\begin{bullets}
  \item Introduced automatic support for right-to-left (RTL) languages to Oleo,
  an internal JS framework for creating ``immersive'' (interactive, app-like)
  search results.

  \item Launched immersive results for TV/music/film queries in Arabic- and
  Hebrew-speaking countries.

  \item Maintained Oleo and added new features used for the Google Trips UI and 
the 2016 Olympics experience.
\end{bullets}

\subsection*{
  \note{\loc{Montreal, QC}\\May 2013 - May 2014}
  \dotsep
  {\textbf{Scheduling Direct}}
  {Frontend Lead}
  {\emph{Tools used:} Backbone.js}
}
\begin{bullets}
  \item Architected and implemented the employee and manager user interfaces for
  a shift-scheduling application.
\end{bullets}

%\subsection*{
%  \note{\loc{New York, NY}\\Summer 2012}
%  \dotsep
%  {\textbf{Boxee}}
%  {Intern}
%  {\emph{Tools used:} D3.js, Backbone.js}
%}
%\begin{bullets}
%  \item Developed interactive social graph visualization tool, used to
%  analyze the growth of a new product.
%\end{bullets}

%\section*{Skills, Activities and Interests}
\section*{Life Experience}

\subsection*{\textbf{Technology Skills}}
Javascript, Typescript, React, Vue, React Native, Python, Django, SQL,
Haskell, Java, Rust, Unix, Git, WebGL

\subsection*{\textbf{Activities}}
\note{May 2018 - Mar 2020}
Converted a cargo van into a mobile home, and lived in it while traveling North
America and rock climbing.

\subsection*{\textbf{Interests}}
Computer graphics, Functional programming, Rock
climbing, Trail running, Snowboarding, Woodworking

\section*{Education}
\note{\textbf{McGill University\\Montreal, QC}\\2010 - 2015}
\subsection*{
  \dotsep
  {\textbf{B.Sc. (with Honours)} Mathematics \amper$\:$ Computer Science}
  {\textbf{Minor} Physics}
  {\textbf{GPA} $3.53$}
}
\emph{Notable coursework:} Logic and Computation, Formal Verification,
Algorithm Design, Topology, Real Analysis
\end{document}
